%%% Author: mterenui (F.M.T.C)
%%% Docs: https://github.com/xxx
%%% License: GNU General Public License v3.0
%%% This document is provided as a general template for informational purposes only and does not constitute legal advice. Permission is granted to copy, modify, and use this template for personal or commercial purposes, provided that this copyright and license notice is retained in all copies or substantial portions of the document. The author makes no representations or warranties regarding the legal validity or enforceability of this template in any jurisdiction. Users are strongly encouraged to consult a qualified legal professional before using this document.

Dear \recipientName{},

This letter serves as a formal cease and desist notice regarding your continued acts of harassment and defamation directed toward me.

It has come to my attention that you have engaged in repeated and unwelcome conduct, including but not limited to \OffenseDescription{}, beginning on or about \OffenseDate{}. In addition, you have made and/or circulated false and defamatory statements about me, including \DefamationDescription{}, which have caused harm to my reputation, emotional distress, and potential personal and professional damage.

\textbf{Your actions constitute:}
\begin{itemize}
  \item \textbf{Harassment}, as they are persistent, unwanted, and intended to intimidate, threaten, or distress; and
  \item \textbf{Defamation}, as the statements made are false, presented as fact, and damaging to my reputation.
\end{itemize}

\textbf{Accordingly, you are hereby directed to immediately cease and desist from:}
\begin{enumerate}
  \item Any form of harassment, contact, or communication with me, whether directly or indirectly;
  \item Making, publishing, repeating, or distributing any false or defamatory statements concerning me;
  \item Encouraging or inducing third parties to engage in such conduct on your behalf.
\end{enumerate}

You are further required to remove, retract, and permanently delete any defamatory content already published or circulated by you, no later than \Deadline{}, and to provide written confirmation of compliance.

Please be advised that failure to comply with this notice may leave me with no alternative but to pursue appropriate legal remedies, including but not limited to civil action, injunctive relief, damages, and recovery of legal costs, without further notice.

This notice is issued without prejudice to my rights and remedies, all of which are expressly reserved.

Kindly govern yourself accordingly.

%%% End of document (content.tex)